### 2024-10-16 basic-statistics.qmd
20241016 - render the figure caption as alt text
20241016 - add alt-text to figures

```{r}
#| layout-ncol: 2
#| fig-cap: "Interpretation of *p*-Values When Examining The Differences Between Groups. The vertical black lines reflect the group means."
#| fig-subcap: 
#|   - "What is the probability my data would look like this..."
#|   - "...if in the population, the groups were really this?"
#| label: fig-pValuesDifference
#| code-fold: true

@@

```{r}
#| layout-ncol: 2
#| fig-cap: "Interpretation of *p*-Values When Examining The Association Between Variables."
#| fig-subcap: 
#|   - "What is the probability my data would look like this..."
#|   - "...if in the population, the association was really this?"
#| label: fig-pValuesAssociation
#| code-fold: true

@@

::: {#fig-nhstConfusionMatrix}
![](images/nhstConfusionMatrix.png)

@@

```{r}
#| label: fig-nhst
#| fig-cap: "Statistical Power (Adapted from Kristoffer Magnusson: <https://rpsychologist.com/creating-a-typical-textbook-illustration-of-statistical-power-using-either-ggplot-or-base-graphics>; archived at <https://perma.cc/FG3J-85L6>). The dashed line represents the critical value or threshold."
#| code-fold: true

@@

::: {#fig-statisticalDecisionTree}
![](images/statisticalDecisionTree.png)

@@

::: {#fig-statisticalDecisionTreeSummary}
![](images/statisticalDecisionTreeSummary.png)

@@

::: {#fig-statisticalDecisionTreeRegression}
![](images/statisticalDecisionTreeRegression.png)

@@

::: {#fig-statisticalDecisionTreeSummaryRegression}
![](images/statisticalDecisionTreeSummaryRegression.png)

>>>>

```{r}
#| layout-ncol: 2
#| fig-cap: "Interpretation of *p*-Values When Examining The Differences Between Groups. The vertical black lines reflect the group means."
#| fig-alt: "Interpretation of *p*-Values When Examining The Differences Between Groups. The vertical black lines reflect the group means."
#| fig-subcap: 
#|   - "What is the probability my data would look like this..."
#|   - "...if in the population, the groups were really this?"
#| label: fig-pValuesDifference
#| code-fold: true

@@

```{r}
#| layout-ncol: 2
#| fig-cap: "Interpretation of *p*-Values When Examining The Association Between Variables."
#| fig-alt: "Interpretation of *p*-Values When Examining The Association Between Variables."
#| fig-subcap: 
#|   - "What is the probability my data would look like this..."
#|   - "...if in the population, the association was really this?"
#| label: fig-pValuesAssociation
#| code-fold: true

@@

::: {#fig-nhstConfusionMatrix}
![](images/nhstConfusionMatrix.png)\

@@

```{r}
#| label: fig-nhst
#| fig-cap: "Statistical Power (Adapted from Kristoffer Magnusson: <https://rpsychologist.com/creating-a-typical-textbook-illustration-of-statistical-power-using-either-ggplot-or-base-graphics>; archived at <https://perma.cc/FG3J-85L6>). The dashed line represents the critical value or threshold."
#| fig-alt: "Statistical Power (Adapted from Kristoffer Magnusson: <https://rpsychologist.com/creating-a-typical-textbook-illustration-of-statistical-power-using-either-ggplot-or-base-graphics>; archived at <https://perma.cc/FG3J-85L6>). The dashed line represents the critical value or threshold."
#| code-fold: true

@@

::: {#fig-statisticalDecisionTree}
![](images/statisticalDecisionTree.png)\

@@

::: {#fig-statisticalDecisionTreeSummary}
![](images/statisticalDecisionTreeSummary.png)\

@@

::: {#fig-statisticalDecisionTreeRegression}
![](images/statisticalDecisionTreeRegression.png)\

@@

::: {#fig-statisticalDecisionTreeSummaryRegression}
![](images/statisticalDecisionTreeSummaryRegression.png)\

### 2024-10-16 causal-inference.qmd
20241016 - add alt-text to figures

```{r}
#| label: fig-XCausesY
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting `X` Causing `Y`."

@@

```{r}
#| label: fig-XCausesY2
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting `X` Causing `Y`."

@@

```{r}
#| label: fig-YCausesX
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting Reverse Causation: `Y` Causing `X`."

@@

```{r}
#| label: fig-YCausesX2
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting Reverse Causation: `Y` Causing `X`."

@@

```{r}
#| label: fig-ZCausesXandY
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting a Third Variable Confound, `Z`, Causing `X` and `Y`, Thus Explaining Why `X` and `Y` are associated."

@@

```{r}
#| label: fig-ZCausesXandY2
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting a Third Variable Confound, `Z`, Causing `X` and `Y`, Thus Explaining Why `X` and `Y` are associated."

@@

```{r}
#| label: fig-dag
#| fig-cap: "Causal Diagram (Directed Acyclic Graph)."

@@

```{r}
#| label: fig-dag2
#| fig-cap: "Causal Diagram (Directed Acyclic Graph)."

@@

```{r}
#| label: fig-counfounding
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Confounding."

@@

```{r}
#| label: fig-fullMediation
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Full Mediation."

@@

```{r}
#| label: fig-partialMediation
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Partial Mediation."

@@

```{r}
#| label: fig-dagDescendant
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Ancestor (Mediation) and Descendant of Y."

@@

```{r}
#| label: fig-colliderBias1
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of a Collision with a Collider (Injury Status)."

@@

```{r}
#| label: fig-colliderBias2
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Collider Bias."

@@

```{r}
#| label: fig-mBias
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of M-Bias."

@@

```{r}
#| label: fig-butterflyBias
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Butterfly Bias."

>>>>

```{r}
#| label: fig-XCausesY
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting `X` Causing `Y`."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Depicting `X` Causing `Y`."

@@

```{r}
#| label: fig-XCausesY2
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting `X` Causing `Y`."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Depicting `X` Causing `Y`."

@@

```{r}
#| label: fig-YCausesX
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting Reverse Causation: `Y` Causing `X`."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Depicting Reverse Causation: `Y` Causing `X`."

@@

```{r}
#| label: fig-YCausesX2
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting Reverse Causation: `Y` Causing `X`."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Depicting Reverse Causation: `Y` Causing `X`."

@@

```{r}
#| label: fig-ZCausesXandY
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting a Third Variable Confound, `Z`, Causing `X` and `Y`, Thus Explaining Why `X` and `Y` are associated."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Depicting a Third Variable Confound, `Z`, Causing `X` and `Y`, Thus Explaining Why `X` and `Y` are associated."

@@

```{r}
#| label: fig-ZCausesXandY2
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Depicting a Third Variable Confound, `Z`, Causing `X` and `Y`, Thus Explaining Why `X` and `Y` are associated."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Depicting a Third Variable Confound, `Z`, Causing `X` and `Y`, Thus Explaining Why `X` and `Y` are associated."

@@

```{r}
#| label: fig-dag
#| fig-cap: "Causal Diagram (Directed Acyclic Graph)."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph)."

@@

```{r}
#| label: fig-dag2
#| fig-cap: "Causal Diagram (Directed Acyclic Graph)."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph)."

@@

```{r}
#| label: fig-counfounding
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Confounding."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Example of Confounding."

@@

```{r}
#| label: fig-fullMediation
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Full Mediation."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Example of Full Mediation."

@@

```{r}
#| label: fig-partialMediation
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Partial Mediation."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Example of Partial Mediation."

@@

```{r}
#| label: fig-dagDescendant
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Ancestor (Mediation) and Descendant of Y."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Example of Ancestor (Mediation) and Descendant of Y."

@@

```{r}
#| label: fig-colliderBias1
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of a Collision with a Collider (Injury Status)."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Example of a Collision with a Collider (Injury Status)."

@@

```{r}
#| label: fig-colliderBias2
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Collider Bias."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Example of Collider Bias."

@@

```{r}
#| label: fig-mBias
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of M-Bias."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Example of M-Bias."

@@

```{r}
#| label: fig-butterflyBias
#| fig-cap: "Causal Diagram (Directed Acyclic Graph) Example of Butterfly Bias."
#| fig-alt: "Causal Diagram (Directed Acyclic Graph) Example of Butterfly Bias."

### 2024-10-16 cluster-analysis.qmd
20241016 - add alt-text to figures

```{r}
#| label: fig-qbTiers
#| fig-cap: "Quarterback Fantasy Points by Tier."

@@

```{r}
#| label: fig-rbTiers
#| fig-cap: "Running Back Fantasy Points by Tier."

@@

```{r}
#| label: fig-wrTiers
#| fig-cap: "Quarterback Fantasy Points by Tier."

@@

```{r}
#| label: fig-teTiers
#| fig-cap: "Tight End Fantasy Points by Tier."

>>>>

```{r}
#| label: fig-qbTiers
#| fig-cap: "Quarterback Fantasy Points by Tier."
#| fig-alt: "Quarterback Fantasy Points by Tier."

@@

```{r}
#| label: fig-rbTiers
#| fig-cap: "Running Back Fantasy Points by Tier."
#| fig-alt: "Running Back Fantasy Points by Tier."

@@

```{r}
#| label: fig-wrTiers
#| fig-cap: "Quarterback Fantasy Points by Tier."
#| fig-alt: "Quarterback Fantasy Points by Tier."

@@

```{r}
#| label: fig-teTiers
#| fig-cap: "Tight End Fantasy Points by Tier."
#| fig-alt: "Tight End Fantasy Points by Tier."

### 2024-10-16 cognitive-bias.qmd
20241016 - render the figure caption as alt text
20241016 - add alt-text to figures

![Video of Kyle Pitts drawing comparisons to the LeBron James of Tight Ends. From: <https://x.com/GetUpESPN/status/1380165126108672001> (archived at <https://perma.cc/JW8E-KV2C>)](images/kylePitts.mp4){width=100%}

@@

::: {#fig-prospectTheory}
![](images/prospectTheory.png)

@@

::: {#fig-dunningKrueger1}
![](images/dunningKrueger_1.png)

@@

::: {#fig-dunningKrueger2}
![](images/dunningKrueger_2.png)

@@

```{r}
#| fig-cap: "Histogram of Number of Coins that Flip Heads-Up in a Simulation of 10 Coin Flips (with 100,000 Replications)."
#| label: fig-simulationOf10CoinFlips
#| code-fold: true

>>>>

![Video of Kyle Pitts drawing comparisons to the LeBron James of Tight Ends. From: <https://x.com/GetUpESPN/status/1380165126108672001> (archived at <https://perma.cc/JW8E-KV2C>)](images/kylePitts.mp4){width=100%}\

@@

::: {#fig-prospectTheory}
![](images/prospectTheory.png)\

@@

::: {#fig-dunningKrueger1}
![](images/dunningKrueger_1.png)\

@@

::: {#fig-dunningKrueger2}
![](images/dunningKrueger_2.png)\

@@

```{r}
#| fig-cap: "Histogram of Number of Coins that Flip Heads-Up in a Simulation of 10 Coin Flips (with 100,000 Replications)."
#| fig-alt: "Histogram of Number of Coins that Flip Heads-Up in a Simulation of 10 Coin Flips (with 100,000 Replications)."
#| label: fig-simulationOf10CoinFlips
#| code-fold: true

### 2024-10-16 correlation.qmd
20240720 - assumptions
20241016 - add alt-text to figures

```{r}
#| label: fig-rangeOfCorrelations
#| fig-cap: "Correlation Coefficients."
#| fig-height: 12
#| code-fold: true
#| message: false

@@

```{r}
#| label: fig-interepretingCorrelationCoefficients
#| fig-cap: "Interpretation of the Magnitude and Direction (Sign) of Correlation Coefficients."
#| fig-height: 9
#| fig-width: 9
#| code-fold: true
#| message: false

@@

## Correlation Does Not Imply Causation

>>>>

```{r}
#| label: fig-rangeOfCorrelations
#| fig-cap: "Correlation Coefficients."
#| fig-alt: "Correlation Coefficients."
#| fig-height: 12
#| code-fold: true
#| message: false

@@

```{r}
#| label: fig-interepretingCorrelationCoefficients
#| fig-cap: "Interpretation of the Magnitude and Direction (Sign) of Correlation Coefficients."
#| fig-alt: "Interpretation of the Magnitude and Direction (Sign) of Correlation Coefficients."
#| fig-height: 9
#| fig-width: 9
#| code-fold: true
#| message: false

@@

## Impact of Outliers {#sec-correlationOutliers}

## Correlation Does Not Imply Causation {#sec-correlation-correlationAndCausation}

### 2024-10-16 data-visualization.qmd
20241016 - add alt-text to figures

```{r}
#| label: fig-exampleDataVisualization
#| fig-cap: "Example Figure that Applies the Principles of Data Visualization."
#| code-fold: true

@@

```{r}
#| label: fig-histogram
#| fig-cap: "Histogram of Fantasy Points."

@@

```{r}
#| label: fig-density
#| fig-cap: "Density Plot of Fantasy Points by Position."

@@

```{r}
#| label: fig-histogramDensity
#| fig-cap: "Histogram with Overlaid Density and Rug Plot."

@@

```{r}
#| label: fig-boxAndWhisker
#| fig-cap: "Box-and-Whisker Plot."

@@

```{r}
#| label: fig-violin
#| fig-cap: "Violin Plot. Lines represent the 25th, 50th, and 75th quantiles."

@@

```{r}
#| label: fig-ridgeline1
#| fig-cap: "Ridgeline Plot."

@@

```{r}
#| label: fig-ridgeline2
#| fig-cap: "Ridgeline Plot. Lines represent the 25th, 50th, and 75th quantiles."

@@

```{r}
#| label: fig-scatterplot1
#| fig-cap: "Base Plot."

@@

```{r}
#| label: fig-scatterplot2
#| fig-cap: "Scatterplot."

@@

```{r}
#| label: fig-scatterplot3
#| fig-cap: "Scatterplot with Linear Best-Fit Line."

@@

```{r}
#| label: fig-scatterplot4
#| fig-cap: "Scatterplot with Quadratic Best-Fit Line."

@@

```{r}
#| label: fig-scatterplot5
#| fig-cap: "Scatterplot with Best-Fit Line Using Locally Estimated Scatterplot Smoothing (LOESS)."

@@

```{r}
#| label: fig-scatterplot6
#| fig-cap: "Scatterplot with Best-Fit Line from Generalized Additive Model."

@@

```{r}
#| label: fig-scatterplot7
#| fig-cap: "Scatterplot with Modified Axes."

@@

```{r}
#| label: fig-scatterplot8
#| fig-cap: "Scatterplot with Plot Labels."

@@

```{r}
#| label: fig-scatterplot9
#| fig-cap: "Scatterplot with Classic Theme."

@@

```{r}
#| label: fig-scatterplot10
#| fig-cap: "Scatterplot with Dark Theme."

@@

```{r}
#| label: fig-scatterplot11
#| fig-cap: "Interactive Scatterplot Using Plotly."

@@

```{r}
#| label: fig-lineChart
#| fig-cap: "Line Chart."

@@

```{r}
#| label: fig-lineChartHighlighting
#| fig-cap: "Line Chart with Highlighting."

@@

```{r}
#| label: fig-barPlot
#| fig-cap: "Bar Plot."

@@

```{r}
#| label: fig-barPlotConfidenceInterval
#| fig-cap: "Bar Plot with Bars Representing the 95% Confidence Interval."

@@

```{r}
#| label: fig-barPlotColorScheme
#| fig-cap: "Bar Plot with Bars Representing the 95% Confidence Interval."

@@

```{r}
#| label: fig-facetedScatterplot
#| fig-cap: "Faceted Scatterplot."

@@

```{r}
#| label: fig-rushYPCperSeasonByAge
#| fig-cap: "Rushing Yards Per Carry (Season) by Player Age."

@@

```{r}
#| label: fig-rushYPCperSeasonByAgePDF
#| fig-cap: "NFL Rushing Yards Per Carry Per Season by Player Age."

@@

```{r}
#| label: fig-rushEPAperSeasonByAge
#| fig-cap: "Rushing Expected Points Added (Season) by Player Age."

@@

```{r}
#| label: fig-rushEPAperSeasonByAgePDF
#| fig-cap: "NFL Rushing Expected Points Added (EPA) During a Season by Player Age."

@@

```{r}
#| label: fig-plotDefOffEPA
#| fig-cap: "2024 NFL Offensive and Defensive EPA Per Play."

>>>>

```{r}
#| label: fig-exampleDataVisualization
#| fig-cap: "Example Figure that Applies the Principles of Data Visualization."
#| fig-alt: "Example Figure that Applies the Principles of Data Visualization."
#| code-fold: true

@@

```{r}
#| label: fig-histogram
#| fig-cap: "Histogram of Fantasy Points."
#| fig-alt: "Histogram of Fantasy Points."

@@

```{r}
#| label: fig-density
#| fig-cap: "Density Plot of Fantasy Points by Position."
#| fig-alt: "Density Plot of Fantasy Points by Position."

@@

```{r}
#| label: fig-histogramDensity
#| fig-cap: "Histogram with Overlaid Density and Rug Plot."
#| fig-alt: "Histogram with Overlaid Density and Rug Plot."

@@

```{r}
#| label: fig-boxAndWhisker
#| fig-cap: "Box-and-Whisker Plot."
#| fig-alt: "Box-and-Whisker Plot."

@@

```{r}
#| label: fig-violin
#| fig-cap: "Violin Plot. Lines represent the 25th, 50th, and 75th quantiles."
#| fig-alt: "Violin Plot. Lines represent the 25th, 50th, and 75th quantiles."

@@

```{r}
#| label: fig-ridgeline1
#| fig-cap: "Ridgeline Plot."
#| fig-alt: "Ridgeline Plot."

@@

```{r}
#| label: fig-ridgeline2
#| fig-cap: "Ridgeline Plot. Lines represent the 25th, 50th, and 75th quantiles."
#| fig-alt: "Ridgeline Plot. Lines represent the 25th, 50th, and 75th quantiles."

@@

```{r}
#| label: fig-scatterplot1
#| fig-cap: "Base Plot."
#| fig-alt: "Base Plot."

@@

```{r}
#| label: fig-scatterplot2
#| fig-cap: "Scatterplot."
#| fig-alt: "Scatterplot."

@@

```{r}
#| label: fig-scatterplot3
#| fig-cap: "Scatterplot with Linear Best-Fit Line."
#| fig-alt: "Scatterplot with Linear Best-Fit Line."

@@

```{r}
#| label: fig-scatterplot4
#| fig-cap: "Scatterplot with Quadratic Best-Fit Line."
#| fig-alt: "Scatterplot with Quadratic Best-Fit Line."

@@

```{r}
#| label: fig-scatterplot5
#| fig-cap: "Scatterplot with Best-Fit Line Using Locally Estimated Scatterplot Smoothing (LOESS)."
#| fig-alt: "Scatterplot with Best-Fit Line Using Locally Estimated Scatterplot Smoothing (LOESS)."

@@

```{r}
#| label: fig-scatterplot6
#| fig-cap: "Scatterplot with Best-Fit Line from Generalized Additive Model."
#| fig-alt: "Scatterplot with Best-Fit Line from Generalized Additive Model."

@@

```{r}
#| label: fig-scatterplot7
#| fig-cap: "Scatterplot with Modified Axes."
#| fig-alt: "Scatterplot with Modified Axes."

@@

```{r}
#| label: fig-scatterplot8
#| fig-cap: "Scatterplot with Plot Labels."
#| fig-alt: "Scatterplot with Plot Labels."

@@

```{r}
#| label: fig-scatterplot9
#| fig-cap: "Scatterplot with Classic Theme."
#| fig-alt: "Scatterplot with Classic Theme."

@@

```{r}
#| label: fig-scatterplot10
#| fig-cap: "Scatterplot with Dark Theme."
#| fig-alt: "Scatterplot with Dark Theme."

@@

```{r}
#| label: fig-scatterplot11
#| fig-cap: "Interactive Scatterplot Using Plotly."
#| fig-alt: "Interactive Scatterplot Using Plotly."

@@

```{r}
#| label: fig-lineChart
#| fig-cap: "Line Chart."
#| fig-alt: "Line Chart."

@@

```{r}
#| label: fig-lineChartHighlighting
#| fig-cap: "Line Chart with Highlighting."
#| fig-alt: "Line Chart with Highlighting."

@@

```{r}
#| label: fig-barPlot
#| fig-cap: "Bar Plot."
#| fig-alt: "Bar Plot."

@@

```{r}
#| label: fig-barPlotConfidenceInterval
#| fig-cap: "Bar Plot with Bars Representing the 95% Confidence Interval."
#| fig-alt: "Bar Plot with Bars Representing the 95% Confidence Interval."

@@

```{r}
#| label: fig-barPlotColorScheme
#| fig-cap: "Bar Plot with Bars Representing the 95% Confidence Interval."
#| fig-alt: "Bar Plot with Bars Representing the 95% Confidence Interval."

@@

```{r}
#| label: fig-facetedScatterplot
#| fig-cap: "Faceted Scatterplot."
#| fig-alt: "Faceted Scatterplot."

@@

```{r}
#| label: fig-rushYPCperSeasonByAge
#| fig-cap: "Rushing Yards Per Carry (Season) by Player Age."
#| fig-alt: "Rushing Yards Per Carry (Season) by Player Age."

@@

```{r}
#| label: fig-rushYPCperSeasonByAgePDF
#| fig-cap: "NFL Rushing Yards Per Carry Per Season by Player Age."
#| fig-alt: "NFL Rushing Yards Per Carry Per Season by Player Age."

@@

```{r}
#| label: fig-rushEPAperSeasonByAge
#| fig-cap: "Rushing Expected Points Added (Season) by Player Age."
#| fig-alt: "Rushing Expected Points Added (Season) by Player Age."

@@

```{r}
#| label: fig-rushEPAperSeasonByAgePDF
#| fig-cap: "NFL Rushing Expected Points Added (EPA) During a Season by Player Age."
#| fig-alt: "NFL Rushing Expected Points Added (EPA) During a Season by Player Age."

@@

```{r}
#| label: fig-plotDefOffEPA
#| fig-cap: "2024 NFL Offensive and Defensive EPA Per Play."
#| fig-alt: "2024 NFL Offensive and Defensive EPA Per Play."

### 2024-10-16 evaluating-prediction-accuracy.qmd
20241016 - add alt-text to figures

```{r}
#| fig-cap: "Distribution of Test Scores by Berry Type."
#| label: fig-classificationDistributions
#| code-fold: true

@@

```{r}
#| fig-cap: "Classifications Based on a Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| label: fig-classificationStandardCutoff
#| code-fold: true

@@

```{r}
#| fig-cap: "Classifications Based on Raising the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| label: fig-classificationRaiseCutoff
#| code-fold: true

@@

```{r}
#| fig-cap: "Classifications Based on Lowering the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| label: fig-classificationLowerCutoff
#| code-fold: true

@@

```{r}
#| fig-cap: "Receiver Operating Characteristic (ROC) Curves for Various Levels of Area Under The ROC Curve (AUC) for Various Measures."
#| label: fig-aucRange
#| fig-width: 8
#| fig-height: 8
#| code-fold: true

@@

```{r}
#| label: fig-calibrationPlot
#| fig-cap: "Predictions that are Well-Calibrated. That is, the predicted values are close to the observed values."
#| fig-width: 8
#| fig-height: 8
#| code-fold: true

@@

```{r}
#| label: fig-miscalibration
#| fig-cap: "Types of Miscalibration. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."
#| fig-width: 8
#| fig-height: 8
#| code-fold: true

>>>>

```{r}
#| fig-cap: "Distribution of Test Scores by Berry Type."
#| fig-alt: "Distribution of Test Scores by Berry Type."
#| label: fig-classificationDistributions
#| code-fold: true

@@

```{r}
#| fig-cap: "Classifications Based on a Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| fig-alt: "Classifications Based on a Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| label: fig-classificationStandardCutoff
#| code-fold: true

@@

```{r}
#| fig-cap: "Classifications Based on Raising the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| fig-alt: "Classifications Based on Raising the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| label: fig-classificationRaiseCutoff
#| code-fold: true

@@

```{r}
#| fig-cap: "Classifications Based on Lowering the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| fig-alt: "Classifications Based on Lowering the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| label: fig-classificationLowerCutoff
#| code-fold: true

@@

```{r}
#| fig-cap: "Receiver Operating Characteristic (ROC) Curves for Various Levels of Area Under The ROC Curve (AUC) for Various Measures."
#| fig-alt: "Receiver Operating Characteristic (ROC) Curves for Various Levels of Area Under The ROC Curve (AUC) for Various Measures."
#| label: fig-aucRange
#| fig-width: 8
#| fig-height: 8
#| code-fold: true

@@

```{r}
#| label: fig-calibrationPlot
#| fig-cap: "Predictions that are Well-Calibrated. That is, the predicted values are close to the observed values."
#| fig-alt: "Predictions that are Well-Calibrated. That is, the predicted values are close to the observed values."
#| fig-width: 8
#| fig-height: 8
#| code-fold: true

@@

```{r}
#| label: fig-miscalibration
#| fig-cap: "Types of Miscalibration. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."
#| fig-alt: "Types of Miscalibration. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."
#| fig-width: 8
#| fig-height: 8
#| code-fold: true
